\Large \bf Webcam Fuzz Testing: Testing IoT Deployments

### 2015-12-05 Draft Paper/Draft_Paper.tex
Merge remote-tracking branch 'origin/master'
# Conflicts:
#	Draft Paper/Draft_Paper.tex

@@

\subsection{Problem}

In this project, we designed, implemented and evaluated an automated tester for a networking service. This is meant to evaluate the value of fuzz testing on a network, with the goal of hopefully finding a previously undiscovered bug. A very basic and highly proliferated technology deployed on the internet is an HTTP server. But because of this prevalence, popular servers such as Apache have been thoroughly tested and documented. However, more and more devices are being connected, with an uptake in the Internet of Things (IoT) mentality. Therefore, we chose wireless IP cameras as the platform to fuzz test. These are some of the most widely available IoT devices for consumers. We found that the two devices we purchased ran basic HTTP servers, and we could use tools made for these applications.

@@

\section{Related Work}
One of the first attempts at a random input tester was done by Miller et. al.~\cite{millerUNIX}. Their work consisted of creating small programs for UNIX that would generate ransom strings that would then be piped to various programs of a few UNIX distributions. They found, at the time of publication in 1990, that they could cause roughly a third of the tested utilities to crash or hang with the generated inputs, some of which even cause UNIX crashes.

@@

While these papers looked like they had gathered results from their fuzz testing, they did not release their prototype to the public, and therefore we had to find other publicly available tools that would be able to create fuzz tests. A few of the papers read, such as AspFuzz, mentioned the Peach Fuzzing Platform~\cite{peach} as a tool widely used in this type of testing. We were also able to find widely available tools like AutoFuzz~\cite{autofuzz}, American Fuzzy Lop (AFL)~\cite{afl}, and Pathod/Pathoc~\cite{pathoc}. More discussion on these tools is presented in section 3.1.2.

??CAN we find a paper or related work where other IoT devices were similarly tested for security vulnerabilities??

@@

\subsection{IP Cameras}
The two cameras we purchased were a D-Link Day \& Night Wi-Fi Camera (DCS-934L)~\cite{dlinkCam} and a Pyle Home Indoor Wireless/Wired P2P IP Network Camera (PIPCAM5). Though both cameras supported many network protocols, we focused on fuzzing the \textit{alphapd} and \textit{mini-httpd} HTTP servers and the application layers of each of the cameras.

@@

Though the cameras boasted support for many network protocols, most of the functionality was very limited and only supported client protocols. Both cameras did have small HTTP servers, though, which are much more interesting to fuzz, as they will more readily accept the inputs that we would give them.

The first step in identifying network protocols that would be interesting and `fuzzable' was to capture some traffic from the cameras in Wireshark~\cite{wireshark}. We also looked at the HTML source behind the web pages to discover potential attack points. We discovered early on that authentication tokens could be easily exposed, making deeper application level access possible. This was possible because the cameras only used Basic Authentication, where the encoded user name and password are store in plaintext in the requests. From here, we could automate the fuzzer to get past the HTTP ``front door" and send sensitive commands that require authentication. This way, we could also test the application layer being run on these camera, rather than the HTTP protocol layer. We discovered several `.cgi' pages under the main HTML pages that were the primary interfaces to the camera functions., and these pages were used to fuzz application layers.

@@

\subsubsection{Tools}
We began by exploring a number of available network fuzzers, including Peach, AutoFuzz, American Fuzzy Lop (AFL), and Pathoc. In investigating AFL, we found that it was a tool mainly for file testing, where good files as inputs to tools would be mutated and input back into a program for evaluation. We could have used this to create a file with a valid GET request, ran AFL to mutate, and send the file through something like netcat, but this would be more difficult to control in what get sent to the servers.

AutoFuzz had built in support for MSN, SMTP, and FTP protocols, and relied on capturing actual traffic in order to create a state machine. While we did find that both of the cameras used in testing supported both SMTP and FTP, they were only clients, and therefore less likely to accept inputs. We were not able to find HTTP support for AutoFuzz, so this method was abandoned.

Peach was another platform that was looked at extensively. The peach platform relies on ``pits" that define the fields in the standard being tested, as well as the procedure that should be used in testing. Their website shows that they have support for protocols such as HTTP, DHCP, IPv4, IPv6, and IoT protocols like CoAP. However, these pits are how this company makes money, and we were not willing to purchase them in order to evaluate if they would work for us or not.

@@

\subsection{Pathoc Structure}
We used Pathoc for crafted malice towards the mini\_httpd and DLink servers. Pathoc has a built in function to do many requests at one time, but we found that this method had all of the GET requests on a single TCP connection, and therefore made it more difficult to diagnose in programs such as Wireshark. Therefore, since Pathoc can easily be implemented using the command line interface, a shell script was used as a wrapper that would invoke Pathoc multiple times, giving a new HTTP request everytime. In this way, we could also control fairly easily the commands for Pathoc to run, instead of having a single command run multiple times.

We wrote a bash script that would take the IP address, camera ID (1=PYLE, 2=DLINK), and number of fuzzing tests as arguments. Each camera had its own set of fuzzing commands, to make more use of the details we gathered from each individual cameras web page.

We also wrote a script to scour the log files and aggregate the total number of responses in various categories. We used some of this data for the Pyle camera to generate tables~\ref{tab:Pyle_Good_CGI} and ~\ref{tab:Pyle_Rand_CGI}.

[EDIT ME]This is where we could describe in more detail specifics about the types of fuzzing we accomplished, the control loop structures of the scripts, categories of data we recorded, pages or applications that we targeted, etc.

@@

[EDIT ME]
As of today [Nov 28,2015] we have run about 18,000 fuzzing tests. We are in the process of aggregating data and trying to understand how best to display it. We have not as of yet found any input that would disable the cameras completely, though some inputs do cause slow downs. Table~\ref{tab:Pyle_Good_CGI} sums up the distribution of three separate test run sizes for CGI commands with good numeric inputs (within range 1-100). Table~\ref{tab:Pyle_Rand_CGI} shows the same number of tests for purely random alpha-numeric commands.

@@

\begin{table}
\centering
	\begin{tabular}{ |c|c|c| }
		\hline
		~ & Ubuntu 12.04 VM & RPi 2\\
		\hline
		\hline
		Time(s) & 3909 & 17555 \\
		Timeouts & 193 & 545  \\
		HTTP 3XX & 0 & 0 \\
		HTTP 4XX & 1227 & 1210 \\
		HTTP 5XX & 65 & 62 \\
		\hline
	\end{tabular}
	\caption{5000 Random CGI commands on the Ubuntu VM and RPi platforms}
	\label{tab:VMvsPi} 
\end{table}

>>>>

[TODO] Revisit this section after the paper has been more fully fleshed out[TODO]

The specific `call for papers' that we target in the presentation of this research is the 9th USENIX Workshop on Offensive Technologies (WOOT '15).

@@

\subsection{Problem}
We began this project with some general understanding of fuzzing as a test tool, but without a clear vision of what network services might be interesting or valuable to fuzz. After an initial period of exploring current research in fuzzing, we settled on the ultimate goal of our project: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} The project involved several steps: choosing a service to test; deciding how to generate random inputs; determining how to distinguish "good" and "bad" test results; implementing the random tester; and evaluating the effectiveness of the test procedure.

In this project, we started with the goal to design, implement and evaluat an automated tester for a networking service. This is meant to evaluate the value of fuzz testing on a network, with the goal of hopefully finding a previously undiscovered bug. A very basic and highly proliferated technology deployed on the internet is an HTTP server. But because of this prevalence, popular servers such as Apache have been thoroughly tested and documented. However, more and more devices are being connected, with an uptake in the Internet of Things (IoT) mentality. Therefore, we chose wireless IP cameras as the platform to fuzz test. These are some of the most widely available IoT devices for consumers. We found that the two devices we purchased ran basic HTTP servers, and we could use tools made for these applications.

@@

\section{Related Work}
In the beginning stages of our project, we explored some recent papers related to fuzzing, to give us a more clear idea of how this test technique is currently implemented and how it is evolving. Some of the more interesting papers we came across are detailed below.

One of the first attempts at a random input tester was done by Miller et. al.~\cite{millerUNIX}. Their work consisted of creating small programs for UNIX that would generate random strings that would then be piped to various programs of a few UNIX distributions. They found, at the time of publication in 1990, that they could cause roughly a third of the tested utilities to crash or hang with the generated inputs, some of which even caused UNIX crashes.

@@

While these papers looked like they had gathered results from their fuzz testing, they did not release their prototype to the public, and therefore we had to find other publicly available tools that would be able to create fuzz tests. A few of the papers read, such as AspFuzz, mentioned the Peach Fuzzing Platform~\cite{peach} as a tool widely used in this type of testing. We were also able to find widely available tools like AutoFuzz~\cite{autofuzz}, American Fuzzy Lop (AFL)~\cite{afl}, and Pathod/Pathoc~\cite{pathod}. More discussion on these tools is presented in section 3.1.2.

We tried to find research related to fuzzing internet-connected devices, but were unable to. Therefore, we thought this might be a good starting point for our research. We thought this would be interesting because more and more `things' are connecting to the internet today, and all of these `Internet of Things' devices have network protocols that would be interesting to test.

@@

\subsection{IP Cameras}
The two cameras we purchased were a D-Link Day \& Night Wi-Fi Camera (DCS-934L)~\cite{dlinkCam} and a Pyle Home Indoor Wireless/Wired P2P IP Network Camera (PIPCAM5). Though both cameras supported many network protocols, we focused on fuzzing the \textit{alphapd} and \textit{mini-httpd} HTTP servers and the application layers of each of the cameras. We thought the HTTP server protocols and application layers would be the most interesting to fuzz. Most of the other protocols supported were only client protocols, which we felt would be less interesting to fuzz, yet still valuable. We leave testing these other protocols for future work.

@@

Though the cameras boasted support for many network protocols, most of the functionality was very limited and only supported client protocols. Both cameras did have small HTTP servers, though, which we felt were much more interesting to fuzz, as they will more readily accept the inputs that we would give them.

The first step we took in identifying network protocols that would be interesting and `fuzzable' was to capture some traffic from the cameras in Wireshark~\cite{wireshark}. We also looked at the HTML source behind the web pages to discover potential attack points. We discovered early on that authentication tokens could be easily exposed, making deeper application level access possible. This was possible because the cameras only used Basic or Digest Authentication, where the encoded user name and password are stored in plain text in the requests. From here, we could automate the fuzzer to get past the HTTP ``front door" and send sensitive commands that require authentication. This way, we could also test the application layer being run on these camera, rather than the HTTP protocol layer. We discovered several `.cgi' pages under the main HTML pages that were the primary interfaces to the camera functions, and we used these pages to fuzz application layers.

@@

\subsubsection{Tools}
We began by exploring a number of available network fuzzers, including Peach, AutoFuzz, American Fuzzy Lop (AFL), and Pathoc. In investigating AFL, we found that it was a tool mainly for file testing, where good files as inputs to tools would be mutated and input back into a program for evaluation. We could have used this to create a file with a valid GET request, ran AFL to mutate, and send the file through something like netcat, but this would be more difficult to control in what gets sent to the servers. This may be a valuable tool for future work in testing the FTP protocols in the cameras.

AutoFuzz has built in support for MSN, SMTP, and FTP protocols, and relied on capturing actual traffic in order to create a state machine. While we did find that both of the cameras used in testing supported both SMTP and FTP, they were only clients, and therefore less likely to accept inputs. We attempted to, but were ultimately not able to capture SMTP or FTP traffic from the cameras. AutoFuzz did not have support for HTTP, so this tool was abandoned.

Peach was another platform that was looked at extensively. The Peach platform relies on ``pits" that define the fields in the standard being tested, as well as the procedure that should be used in testing. Their website shows that they have support for protocols such as HTTP, DHCP, IPv4, IPv6, and IoT protocols like CoAP. However, these pits are how this company makes money, and we were not willing to purchase them in order to evaluate if they would work for us or not.

@@

\subsection{Pathoc}
We used Pathoc for crafted malice towards the mini\_httpd and alphapd servers. Pathoc has a built in function to do many requests at one time, but we found that this method had all of the GET requests on a single TCP connection, and therefore made it more difficult to diagnose in programs such as Wireshark. Therefore, since Pathoc can easily be implemented using the command line interface, a shell script was used as a wrapper that would invoke Pathoc multiple times, giving a new HTTP request everytime. In this way, we could also control fairly easily the commands for Pathoc to run, instead of having a single command run multiple times.

\subsection{Scripts}
We wrote a Bash script that would take the IP address, camera ID (1=PYLE, 2=DLINK), and number of fuzzing tests as arguments. Each camera had its own set of fuzzing commands, to make more use of the details we gathered from each individual camera's web page.

A short example from our script is shown below. We used variables to control the inputs to the pathoc command. For example \textit{\$cmd} might represent an HTTP GET or POST, \textit{\$b1} represents the contents of the HTTP body, and \textit{\$auth} represents the header with authentication credentials. The output is checked, and server responses with \textbf{HTTP/1.1 200} are marked `good' and all others are marked `bad'. 
\begin{verbatim}
for (( i=1; i<=$max; i++ ))
do	
d=$(( ($i*100)/$max ))
r=$(( $RANDOM % 100 + 1 )) #Random [1..100]

pathoc -n 1 -t 5 -e -p -q $ip "$cmd$r$b1$auth"
 | tee -a "log_$NOW".txt | tee last_cmd.txt
 | grep 'HTTP/1.1 200' &> /dev/null

if [ $? == 0 ]; then
good=$(( $good+1 ))
#last_out=$(<last_cmd.txt)
#echo "$last_out" >> "log_$NOW""_good.txt"
else
bad=$(( $bad+1 ))
last_out=$(<last_cmd.txt)
echo "$last_out" >> "log_$NOW""_bad.txt"
fi		
echo -ne "Percent Done: $d  \tGood: $good   
\tBad: $bad \r"
done
\end{verbatim}

It is important to note that if the server doesn't respond with \textbf{HTTP/1.1 200}, it does not necessarily mean that it is bad. This is just the metric we used to try and identify possible interesting responses. Some interesting responses we found are detailed in the Results section. Both cameras were tested with and without authorization credentials, in an effort to identify possible security vulnerabilities.

Fuzzing directed towards the Pyle camera was focused mainly on the \textit{decoder\_control.cgi} page with various commands. We tried commands with valid numbers, invalid (large or negative) numbers, and random strings of various length.

Fuzzing directed towards the DLink camera were focused in several different categories, including: valid requests sprinkled with random characters, long (70,000 byte) headers, long (70,000 byte) bodies, long (70,000 byte) HTTP GET requests, and HTTP POST to the \textit{audiocontrol.cgi} and \textit{nightmodecontrol.cgi} pages with valid and invalid command bodies.

We also wrote a separate script to scour the log files and aggregate the total number of responses in various categories. We used some of this data for the Pyle camera to generate tables~\ref{tab:Pyle_Good_CGI} and ~\ref{tab:Pyle_Rand_CGI}.

@@

We needed a method of weeding out the `good' responses from the `bad' responses. We decided to look at the several categories of HTTP responses: 
\begin{enumerate}
\item HTTP 2xx - successfully received, understood, and accepted.
\item HTTP 3xx - redirection, or further action required to fulfill request.
\item HTTP 4xx - client error, or some sort of bad request
\item HTTP 5xx - server is aware that it has erred or is incapable of fulfilling request.
\end{enumerate}
We decided to categorize all but HTTP 2xx responses as `bad'. We also discovered other interesting events:
\begin{enumerate}
	\item Response timeouts - pathoc was able to issue the HTTP request but the server didn't respond within the specified time frame.
	\item Connection timeouts - pathoc could not establish a TCP connection with the server after attempting for some period of time.
	\item Invalid server response: Server disconnect
	\item (null) - The server responded but left the identifier blank.
\end{enumerate}

[EDIT ME]
As of today [Dec 4,2015] we have run more than 250,700 fuzzing tests. We are in the process of aggregating data and trying to understand how best to display it. We have not as of yet found any input that would disable the cameras completely, though some inputs do cause slow downs. Some of the interesting events like connection timeouts may be much more interesting if we could determine that the reason the connection could not be made was that the server had been disabled or was restarting itself. There is future work in further analyzing the data that we have collected. We have the log files that show the inputs that generated these responses. Future work would be to gather and replay these inputs and scrutinize the outputs further.

Table~\ref{tab:Pyle_Good_CGI} sums up the distribution of three separate test run sizes for CGI commands with good numeric inputs (within range 1-100). Table~\ref{tab:Pyle_Rand_CGI} shows the same number of tests for purely random alpha-numeric commands.

@@

\begin{table}[here]
\centering
	\begin{tabular}{ |c|c|c| }
		\hline
		~ & Ubuntu 12.04 VM & RPi 2\\
		\hline
		\hline
		Time(s) & 3909 & 17555 \\
		Timeouts & 193 & 545  \\
		HTTP 3XX & 0 & 0 \\
		HTTP 4XX & 1227 & 1210 \\
		HTTP 5XX & 65 & 62 \\
		\hline
	\end{tabular}
	\caption{5000 Random CGI commands on the Ubuntu VM and RPi platforms}
	\label{tab:VMvsPi} 
\end{table}
